---
title: "Wild data"
format: html
editor: visual
execute: 
  warning: false
  output: false
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(janitor)
library(here)
library(ggthemes)
library(ggplot2)
library(dplyr)
```

```{r}
mack_verts <- read.csv(here::here("data","AS00601.csv")) %>% clean_names()
```

```{r}
mc_wt_5 <- mack_verts$weight[5]
mc_wt_5

mc_length_8_20 <- mack_verts$length1[8:20]
mc_length_8_20

mc_dates <- mack_verts$sampledate
mc_dates

```

-   Create a subset that only contains observations for Pacific Giant Salamanders (species *Dicamptodon tenebrosus*, stored in `species` as `DITE`). Store the subset as `mc_salamanders`. *Hint:* see `dplyr::filter()`!

```{r}
mc_salamanders <- mack_verts %>% filter(species == "DITE")
mc_salamanders
```

Create a scatterplot of length1 (snout-vent length in millimeters) versus weight (grams) for all salamanders in the subset you created above, mc_salamanders. Update axis labels, title, subtitle, and add a caption with the data source. Customize point color and size, possibly opacity, and theme.

Export your scatterplot as salamander_size.png to your figs folder.

```{r}
ggplot(data = mc_salamanders, aes(
  x = weight,
  y = length1,
  alpha = weight,
  color = species
)) + geom_point(size = 4) + theme_solarized() +
  scale_colour_solarized("blue") + labs(
    title = 'Pacific Giant Salamanders',
    subtitle = "DITE Snout Length",
    caption = "Gregory, S.V. and I. Arismendi. 2020. 
    Aquatic Vertebrate Population Study in Mack Creek, 
    Andrews Experimental Forest, 
    1987 to present ver 14. 
    Environmental Data Initiative. 
    https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165
    (Accessed 2022-08-10).",
    x = "Weight (g)",
    y = "Length (mm)",
    color = "Species"
  ) 
# ?scale_colour_solarized
# Ask about alpha in aes vs alpha in geom_point, added scale on side
# why does color= species in aes make it blue instead of black

```

```{r}
ggsave(here::here("docs","salamander_size.png"))
```

#### **Make a cutthroat plot**

-   Similar to above, make a subset called `mc_trout` that only contains observations for cutthroat trout (species \"ONCL\")

-   Create a scatterplot of length1 by weight for all trout in the dataset

-   Customize so that the point color depends on *reach*

-   Customize your color scheme (e.g. `scale_color_manual()`)

-   Facet your plot by creek reach (`facet_wrap(~...)`)

-   Update graph axis labels and title

-   Export your graph as `cutthroat_size.png` to the `figs` folder

```{r}
mc_trout <- mack_verts %>% filter(species == "ONCL")



ggplot(data = mc_trout,
       aes(x = weight, y = length1, color = reach)) +
  geom_point() +
  scale_color_manual(values = c("black", "red", "green")) +
  facet_wrap( ~reach) +
  labs(
    title = "Cutthroat Trout",
    subtitle = "Species ONCL Snout Vent Length",
    x = "Weight (g)",
    y = "Length (mm)",
    caption = "Gregory, S.V. and I. Arismendi. 2020.
    Aquatic Vertebrate Population Study in Mack Creek,
    Andrews Experimental Forest,
    1987 to present ver 14.
    Environmental Data Initiative.
    https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165
    (Accessed 2022-08-10).") +
  theme_calc()
ggsave(here::here("docs","cutthroat_size.png"))
```
